systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-02 paper/trunk/JSS/response_B.tex

At the time the package was originally introduced (2002), there were
very few econometrics functions for R and only recently have more
functions and packages been submitted. Adding these functions to an
existing econometrics package would have made sense, had one been
available.

\section{Specific comments}
% Specific comments

\subsection{Instrumental variable estimation}
% Instrumental variable estimation has received much attention lately
% in biostatistics. Maybe it would help 'sell' systemfit if this was
% emphasized at bit more. For instance, instrumental variables could
% be mentioned directly in the introduction and included as a key
% word.

We have mentioned °instrumental variables° in the abstract, included
three examples of topics that use IV methods and have added
°instrumental variables° to the keywords.

### 2007-07-03 paper/trunk/systemfit_statistics.tex
added some references that describe simultaneous equation systems
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@784 591db2bd-e0a0-4d22-8c19-2192dbb7da31

In this section we provide the statistical background
of the functionality provided by the \pkg{systemfit} package.
After introducing notations and assumptions,
we provide the formulas to estimate systems of linear equations.
We then demonstrate how to impose linear restrictions on parameters.
Finally, we present additional relevant issues about estimation of
equation systems.

>>>>

In this section we give a short overview of the statistical background
on that the \pkg{systemfit} package is based on.
More detailed descriptions of simultaneous equations systems
are available for instance in
\citet[chapter~7]{theil71}
\citet[part~4]{judge82}
\citet[part~5]{judge85}
\citet{srivastava87},
\citet[chapters 14--15]{greene03}, and
\citet[chapter~10]{zivot06}.
After introducing notations and assumptions,
we provide the formulas to estimate systems of linear equations.
We then demonstrate how to impose linear restrictions on parameters.
Finally, we present additional relevant issues about estimation of
equation systems.
